---
title: "Old Faithful"
format: 
  html:
    code-tools: 
      source: https://github.com/quarto-dev/quarto-web/tree/main/docs/interactive/shiny/_examples/old-faithful/shiny-old-faithful.qmd
server: shiny
author: Luis Silva, Karen Stalin, Abbey Staugaitis
---

```{r}
#| context: setup
library(ggplot2)
library(tidyverse)
library(dplyr)
unlabelled <- read.csv("https://raw.githubusercontent.com/silva364/StrokeNetSurvey/main/StrokeNetWorkflowSur_DATA_2023-10-03_1610.csv")

```

Welcome to your interactive report of the StrokeNet survey! Here you will be able to generate full a pdf file containing the results from your Regional Coordinating Center (RCC) as compared to the rest of survey responders.

Let's first take a look at the RCCs that anwsered our initial Survey:

```{r}
#| echo: false
rccs <- unlabelled %>%
  group_by(rcc_name) %>%
  count(rcc_name) %>%
  rename(`Regional Coordinating Center` = 1,
         `Number of sites ansering the survey` = 2)

```

The data consists of 299 pairs of measurements, referring to the time interval
between the starts of successive eruptions and the duration of the subsequent
eruption.

Click the **Code** button above to see the source code for this example.

```{r}
#| context: server
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```
